
	\bibitem{wang2024physics}
	Wang X, Xu Y, Liu S, et al. Physics-based fluid simulation in computer graphics: Survey, research trends, and challenges[J]. Computational Visual Media, 2024: 1-56.

	\bibitem{gingold1977smoothed}
	Gingold R A, Monaghan J J. Smoothed particle hydrodynamics: theory and application to non-spherical stars[J]. Monthly Notices of the Royal Astronomical Society, 1977, 181(3): 375-389.

	\bibitem{monaghan2005smoothed}
	Monaghan J J. Smoothed particle hydrodynamics[J]. Reports on Progress in Physics, 2005, 68(8): 1703.

	\bibitem{koschier2022survey}
	Koschier D, Bender J, Solenthaler B, et al. A survey on SPH methods in computer graphics[C]//Computer graphics forum: 2022: 737-760.

	\bibitem{ma2024hybrid}
	Ma Y, Xiao X, Li W, et al. Hybrid LBM-FVM solver for two-phase flow simulation[J]. Journal of Computational Physics, 2024, 506: 112920.

	\bibitem{liu2018adaptive}
	Liu C, Hu C. An adaptive multi-moment FVM approach for incompressible flows[J]. Journal of Computational Physics, 2018, 359: 239-262.

	\bibitem{becker2007weakly}
	Becker M, Teschner M. Weakly compressible SPH for free surface flows[C]//Proceedings of the 2007 ACM SIGGRAPH/Eurographics symposium on Computer animation: 2007: 209-217.

	\bibitem{solenthaler2009predictive}
	Solenthaler B, Pajarola R. Predictive-corrective incompressible SPH[C]//ACM SIGGRAPH 2009 papers: 2009: 1-6.

	\bibitem{bender2015divergence}
	Bender J, Koschier D. Divergence-free smoothed particle hydrodynamics[C]//Proceedings of the 14th ACM SIGGRAPH/Eurographics symposium on computer animation: 2015: 147-155.

	\bibitem{takahashi2023multilevel}
	Takahashi T, Batty C. A multilevel active-set preconditioner for box-constrained pressure poisson solvers[J]. Proceedings of the ACM on Computer Graphics and Interactive Techniques, 2023, 6(3): 1-22.

	\bibitem{hirasawa2021flux}
	Hirasawa N, Kanai T, Ando R. A flux-interpolated advection scheme for fluid simulation[J]. The Visual Computer, 2021, 37(9-11): 2607-2618.

	\bibitem{akinci2013versatile}
	Akinci N, Akinci G, Teschner M. Versatile surface tension and adhesion for SPH fluids[J]. ACM Transactions on Graphics (TOG), 2013, 32(6): 1-8.

	\bibitem{jeske2023implicit}
	Jeske SR, Westhofen L, Loschner F, et al. Implicit Surface Tension for SPH Fluid Simulation[J]. ACM Transactions on Graphics, 2023, 43(1): 1-14.

	\bibitem{feng2022impulse}
	Feng F, Liu J, Xiong S, et al. Impulse fluid simulation[J]. IEEE Transactions on Visualization and Computer Graphics, 2022.

	\bibitem{schechter2012ghost}
	Schechter H, Bridson R. Ghost SPH for animating water[J]. ACM Transactions on Graphics (TOG), 2012, 31(4): 1-8.

	\bibitem{brookshaw1985method}
	Brookshaw L. A method of calculating radiative heat diffusion in particle simulations[J]. Publications of the Astronomical Society of Australia, 1985, 6(2): 207-210.

	\bibitem{takahashi2015implicit}
	Takahashi T, Dobashi Y, Fujishiro I, et al. Implicit formulation for SPH-based viscous fluids[C]//Computer Graphics Forum: 2015: 493-502.

	\bibitem{peer2015implicit}
	Peer A, Ihmsen M, Cornelis J, et al. An implicit viscosity formulation for SPH fluids[J]. ACM Transactions on Graphics (TOG), 2015, 34(4): 1-10.

	\bibitem{weiler2018physically}
	Weiler M, Koschier D, Brand M, et al. A physically consistent implicit viscosity solver for SPH fluids[C]//Computer Graphics Forum: 2018: 145-155.

	\bibitem{goldade2019adaptive}
	Goldade R, Wang Y, Aanjaneya M, et al. An adaptive variational finite difference framework for efficient symmetric octree viscosity[J]. ACM Transactions on Graphics (TOG), 2019, 38(4): 1-14.

	\bibitem{shao2022fast}
	Shao H, Huang L, Michels DL. A fast unsmoothed aggregation algebraic multigrid framework for the large-scale simulation of incompressible flow[J]. ACM Transactions on Graphics (TOG), 2022, 41(4): 1-18.

	\bibitem{bender2016divergence}
	Bender J, Koschier D. Divergence-free SPH for incompressible and viscous fluids[J]. IEEE Transactions on Visualization and Computer Graphics, 2016, 23(3): 1193-1206.

	\bibitem{liu2021adapted}
	Liu S, He X, Wang W, et al. Adapted SIMPLE Algorithm for Incompressible SPH Fluids With a Broad Range Viscosity[J]. IEEE Transactions on Visualization and Computer Graphics, 2021, 28(9): 3168-3179.

	\bibitem{panuelos2023polystokes}
	Panuelos J, Goldade R, Grinspun E, et al. PolyStokes: A polynomial model reduction method for viscous fluid simulation[J]. ACM Transactions on Graphics (TOG), 2023, 42(4): 1-13.

	\bibitem{green2010particle}
	Green S. Particle simulation using cuda[J]. NVIDIA whitepaper, 2010, 6: 121-128.

	\bibitem{bridson2007fast}
	Bridson R. Fast Poisson disk sampling in arbitrary dimensions.[J]. SIGGRAPH sketches, 2007, 10(1): 1.

	\bibitem{cross65}
	Cross M M. Rheology of non-Newtonian fluids: a new flow equation for pseudoplastic systems[J]. Journal of Colloid Science, 1965.

	\bibitem{carreau1972rheological}
	Carreau P J. Rheological equations from molecular network theories[J]. Transactions of the Society of Rheology, 1972, 16(1): 99-127.

	\bibitem{andrade2014sph}
	Andrade LFDS, Sandim M, Petronetto F, et al. SPH fluids for viscous jet buckling[C]//2014 27th SIBGRAPI Conference on Graphics, Patterns and Images: 2014: 65-72.

	\bibitem{ozgen2019sph}
	Ozgen O, Kallmann M, Brown E. An SPH model to simulate the dynamic behavior of shear thickening fluids[J]. Computer Animation and Virtual Worlds, 2019, 30(5): e1870.

	\bibitem{zhu2015codimensional}
	Zhu B, Lee M, Quigley E, et al. Codimensional non-Newtonian fluids[J]. ACM Transactions on Graphics (TOG), 2015, 34(4): 1-9.

	\bibitem{su2021unified}
	Su H, Xue T, Han C, et al. A unified second-order accurate in time MPM formulation for simulating viscoelastic liquids with phase change[J]. ACM Transactions on Graphics (TOG), 2021, 40(4): 1-18.

	\bibitem{li2023unified}
	Li C, Gao Y, He J, et al. A Unified Particle-Based Solver for Non-Newtonian Behaviors Simulation[J]. IEEE Transactions on Visualization and Computer Graphics, 2023.

	\bibitem{oldroyd1950formulation}
	Oldroyd JG. On the formulation of rheological equations of state[J]. Proceedings of the Royal Society of London. Series A. Mathematical and Physical Sciences, 1950, 200(1063): 523-541.

	\bibitem{balci2011symmetric}
	Balci N, Thomases B, Renardy M, et al. Symmetric factorization of the conformation tensor in viscoelastic fluid models[J]. Journal of Non-Newtonian Fluid Mechanics, 2011, 166(11): 546-553.

	\bibitem{bejan2005constructal}
	Bejan A. The constructal law of organization in nature: tree-shaped flows and body size[J]. Journal of Experimental Biology, 2005, 208(9): 1677-1686.

	\bibitem{fattal2005time}
	Fattal R, Kupferman R. Time-dependent simulation of viscoelastic flows at high Weissenberg number using the log-conformation representation[J]. Journal of Non-Newtonian Fluid Mechanics, 2005, 126(1): 23-37.

	\bibitem{coronado2007simple}
	Coronado OM, Arora D, Behr M, et al. A simple method for simulating general viscoelastic fluid flows with an alternate log-conformation formulation[J]. Journal of Non-Newtonian Fluid Mechanics, 2007, 147(3): 189-199.

	\bibitem{afonso2009log}
	Afonso A, Oliveira PJ, Pinho F, et al. The log-conformation tensor approach in the finite-volume method framework[J]. Journal of Non-Newtonian Fluid Mechanics, 2009, 157(1-2): 55-65.

	\bibitem{moreno2019logarithmic}
	Moreno L, Codina R, Baiges J, et al. Logarithmic conformation reformulation in viscoelastic flow problems approximated by a VMS-type stabilized finite element formulation[J]. Computer Methods in Applied Mechanics and Engineering, 2019, 354: 706-731.

	\bibitem{barreiro2017conformation}
	Barreiro H, Garca-Fernandez I, Alduan I, et al. Conformation constraints for efficient viscoelastic fluid simulation[J]. ACM Transactions on Graphics (TOG), 2017, 36(6): 1-11.

	\bibitem{alduan2017dyverso}
	Alduan I, Tena A, Otaduy MA. Dyverso: A versatile multi-phase position-based fluids solution for VFX[C]//Computer Graphics Forum: 2017: 32-44.

	\bibitem{solenthaler2008density}
	Solenthaler B, Pajarola R. Density contrast SPH interfaces[J]. 2008.

	\bibitem{zhang2008material}
	Zhang DZ, Zou Q, VanderHeyden WB, et al. Material point method applied to multiphase flows[J]. Journal of Computational Physics, 2008, 227(6): 3159-3173.

	\bibitem{yan2018mpm}
	Yan X, Li CF, Chen XS, et al. MPM simulation of interacting fluids and solids[C]//Computer Graphics Forum: 2018: 183-193.

	\bibitem{da2014multimaterial}
	Da F, Batty C, Grinspun E. Multimaterial mesh-based surface tracking.[J]. ACM Trans. Graph., 2014, 33(4): 112-1.

	\bibitem{misztal2013multiphase}
	Misztal MK, Erleben K, Bargteil A, et al. Multiphase flow of immiscible fluids on unstructured moving meshes[J]. IEEE transactions on visualization and computer graphics, 2013, 20(1): 4-16.

	\bibitem{li2015multiphase}
	Li X, He X, Liu X, et al. Multiphase interface tracking with fast semi-Lagrangian contouring[J]. IEEE Transactions on Visualization and Computer Graphics, 2015, 22(8): 1973-1986.

	\bibitem{yang2018semi}
	Yang M, Ye J, Ding F, et al. A semi-explicit surface tracking mechanism for multi-phase immiscible liquids[J]. IEEE Transactions on Visualization and Computer Graphics, 2018, 25(10): 2873-2885.

	\bibitem{Mikko96}
	Manninen M, Taivassalo V, Kallio S. On the mixture model for multiphase flow[R]. VTT Publications, 1996(288): 3-67.

	\bibitem{ren2014multiple}
	Ren B, Li C, Yan X, et al. Multiple-fluid SPH simulation using a mixture model[J]. ACM Transactions on Graphics (TOG), 2014, 33(5): 1-11.

	\bibitem{yan2016multiphase}
	Yan X, Jiang YT, Li CF, et al. Multiphase SPH simulation for interactive fluids and solids[J]. ACM Transactions on Graphics (TOG), 2016, 35(4): 1-11.

	\bibitem{ren2021unified}
	Ren B, Xu B, Li C. Unified particle system for multiple-fluid flow and porous material[J]. ACM Transactions on Graphics (TOG), 2021, 40(4): 1-14.

	\bibitem{jiang2020divergence}
	Jiang Y, Li C, Deng S, et al. A Divergence-free Mixture Model for Multiphase Fluids[C]//Computer Graphics Forum: 2020: 69-77.

	\bibitem{jiang2021dynamic}
	Jiang Y, Lan Y. A Dynamic Mixture Model for Non-equilibrium Multiphase Fluids[C]//Computer Graphics Forum: 2021: 85-95.

	\bibitem{xu2023implicitly}
	Xu Y, Wang X, Wang J, et al. An Implicitly Stable Mixture Model for Dynamic Multi-fluid Simulations[C]//SIGGRAPH Asia 2023 Conference Papers: 2023: 1-11.

	\bibitem{hong2003animation}
	Hong JM, Kim CH. Animation of bubbles in liquid[C]//Computer Graphics Forum: 2003: 253-262.

	\bibitem{ihmsen2011animation}
	Ihmsen M, Bader J, Akinci G, et al. Animation of air bubbles with SPH[C]//International Conference on Computer Graphics Theory and Applications: 2011: 225-234.

	\bibitem{takahashi2003realistic}
	Takahashi T, Fujii H, Kunimatsu A, et al. Realistic animation of fluid with splash and foam[C]//Computer Graphics Forum: 2003: 391-400.

	\bibitem{muller2004point}
	Muller M, Keiser R, Nealen A, et al. Point based animation of elastic, plastic and melting objects[C]//Proceedings of the 2004 ACM SIGGRAPH/Eurographics symposium on Computer animation: 2004: 141-151.

	\bibitem{chang2009particle}
	Chang Y, Bao K, Liu Y, et al. A particle-based method for viscoelastic fluids animation[C]//Proceedings of the 16th ACM symposium on virtual reality software and technology: 2009: 111-117.

	\bibitem{fujisawa2007animation}
	Fujisawa M, Miura KT. Animation of ice melting phenomenon based on thermodynamics with thermal radiation[C]//Proceedings of the 5th international conference on Computer graphics and interactive techniques in Australia and Southeast Asia: 2007: 249-256.

	\bibitem{kim2003visual}
	Kim T, Lin MC. Visual simulation of ice crystal growth[C]//Proceedings of the 2003 ACM SIGGRAPH/Eurographics symposium on Computer animation: 2003: 86-97.

	\bibitem{kim2004hybrid}
	Kim T, Henson M, Lin MC. A hybrid algorithm for modeling ice formation[C]//Proceedings of the 2004 ACM SIGGRAPH/Eurographics symposium on Computer animation: 2004: 305-314.

	\bibitem{kim2006modeling}
	Kim T, Adalsteinsson D, Lin MC. Modeling ice dynamics as a thin-film stefan problem[C]//Symposium on Computer Animation: Proceedings of the 2006 ACM SIGGRAPH/Eurographics symposium on Computer animation: Vienna, Austria: 2006: 167-176.

	\bibitem{mihalef2009simulation}
	Mihalef V, Metaxas D, Sussman M. Simulation of two-phase flow with sub-scale droplet and bubble effects[C]//Computer Graphics Forum: 2009: 229-238.

	\bibitem{ren2015simple}
	Ren B, Jiang Y, Li C, et al. A simple approach for bubble modelling from multiphase fluid simulation[J]. Computational Visual Media, 2015, 1: 171-181.

	\bibitem{stomakhin2014augmented}
	Stomakhin A, Schroeder C, Jiang C, et al. Augmented MPM for phase-change and varied materials[J]. ACM Transactions on Graphics (TOG), 2014, 33(4): 1-11.

	\bibitem{tu2024unified}
	Tu Z, Li C, Zhao Z, et al. A Unified MPM Framework Supporting Phase-field Models and Elastic-viscoplastic Phase Transition[J]. ACM Transactions on Graphics, 2024, 43(2): 1-19.

	\bibitem{yang2015fast}
	Yang T, Chang J, Ren B, et al. Fast multiple-fluid simulation using Helmholtz free energy[J]. ACM Transactions on Graphics (TOG), 2015, 34(6): 1-11.

	\bibitem{yan2023high}
	Yan H, Ren B. High Density Ratio Multi-Fluid Simulation with Peridynamics[J]. ACM Transactions on Graphics (TOG), 2023, 42(6): 1-14.

	\bibitem{li2024kinetic}
	Li W, Wu K, Desbrun M. Kinetic simulation of turbulent multifluid flows[J]. ACM Transactions on Graphics (TOG), 2024, 43(4): 1-17.

	\bibitem{li2022efficient}
	Li W, Ma Y, Liu X, et al. Efficient kinetic simulation of two-phase flows[J]. ACM Transactions on Graphics, 2022, 41(4): 114.

	\bibitem{ishii1990two}
	Ishii M. Two-fluid model for two-phase flow[J]. Multiphase science and technology, 1990, 5(1-4).

	\bibitem{larionov2017variational}
	Larionov E, Batty C, Bridson R. Variational stokes: A unified pressure-viscosity solver for accurate viscous liquids[J]. ACM Transactions on Graphics (TOG), 2017, 36(4): 1-11.

	\bibitem{xing2022position}
	Xing J, Ruan L, Wang B, et al. Position-based surface tension flow[J]. ACM Transactions on Graphics (TOG), 2022, 41(6): 1-12.

	\bibitem{macklin2013position}
	Macklin M, Muller M. Position based fluids[J]. ACM Transactions on Graphics (TOG), 2013, 32(4): 1-12.

	\bibitem{macklin2016xpbd}
	Macklin M, Muller M, Chentanez N. XPBD: position-based simulation of compliant constrained dynamics[C]//Proceedings of the 9th International Conference on Motion in Games: 2016: 49-54.

	\bibitem{hochstetter2017evaporation}
	Hochstetter H, Kolb A. Evaporation and condensation of SPH-based fluids[C]//Proceedings of the ACM SIGGRAPH/Eurographics Symposium on Computer Animation: 2017: 1-9.

	\bibitem{fei2019multi}
	Fei Y, Batty C, Grinspun E, et al. A multi-scale model for coupling strands with shear-dependent liquid[J]. ACM Transactions on Graphics (TOG), 2019, 38(6): 1-20.

	\bibitem{li2023fluid}
	Li W, Desbrun M. Fluid-Solid Coupling in Kinetic Two-Phase Flow Simulation[J]. ACM Transactions on Graphics, 2023, 42(4): 1-14.

	\bibitem{bird1987dynamics}
	Bird RB, Armstrong RC, Hassager O. Dynamics of polymeric liquids. Vol. 1: Fluid mechanics[J]. 1987.

	\bibitem{john2024comparison}
	John T, Poole R, Kowalski A, et al. A comparison between the FENE-P and sPTT constitutive models in large-amplitude oscillatory shear[J]. Journal of Fluid Mechanics, 2024, 979: A10.

	\bibitem{renardy2021mathematician}
	Renardy M, Thomases B. A mathematician’s perspective on the Oldroyd B model: progress and future challenges[J]. Journal of Non-Newtonian Fluid Mechanics, 2021, 293: 104573.

	\bibitem{zhang2024multiphase}
	Zhang Y, Long S, Xu Y, et al. Multiphase Viscoelastic Non-Newtonian Fluid Simulation[C]//Computer Graphics Forum: 2024: e15180.

	\bibitem{wyart2014discontinuous}
	Wyart M, Cates ME. Discontinuous shear thickening without inertia in dense non-Brownian suspensions[J]. Physical review letters, 2014, 112(9): 098302.

	\bibitem{royer2016rheological}
	Royer JR, Blair DL, Hudson SD. Rheological signature of frictional interactions in shear thickening suspensions[J]. Physical review letters, 2016, 116(18): 188301.

	\bibitem{hermes2016unsteady}
	Hermes M, Guy BM, Poon WC, et al. Unsteady flow and particle migration in dense, non-Brownian suspensions[J]. Journal of Rheology, 2016, 60(5): 905-916.

	\bibitem{ShenUnifiedMCT}
	Shen L, Zhang Y, Frey S, et al. A unified viscoelastic solver for multiphase fluid simulation based on a mixture model[Z]. Unpublished manuscript.

	\bibitem{vaishya2013bone}
	Vaishya R, Chauhan M, Vaish A. Bone cement[J]. Journal of clinical orthopaedics and trauma, 2013, 4(4): 157-163.

	\bibitem{saha1984mechanical}
	Saha S, Pal S. Mechanical properties of bone cement: a review[J]. Journal of biomedical materials research, 1984, 18(4): 435-462.

	\bibitem{charnley1960anchorage}
	Charnley J. Anchorage of the femoral head prosthesis to the shaft of the femur[J]. The Journal of Bone \& Joint Surgery British Volume, 1960, 42(1): 28-30.

	\bibitem{truumees2004percutaneous}
	Truumees E, Hilibrand A, Vaccaro AR. Percutaneous vertebral augmentation[J]. The Spine Journal, 2004, 4(2): 218-229.

	\bibitem{ebeling2019efficacy}
	Ebeling PR, Akesson K, Bauer DC, et al. The efficacy and safety of vertebral augmentation: a second ASBMR task force report[J]. Journal of Bone and Mineral Research, 2019, 34(1): 3-21.

	\bibitem{breusch2005pulmonary}
	Breusch S, Malchau H, Clarius M, et al. Pulmonary embolism in cemented total hip arthroplasty[J]. The Well-Cemented Total Hip Arthroplasty: Theory and Practice, 2005, 320-331.

	\bibitem{moussazadeh2015short}
	Moussazadeh N, Rubin DG, McLaughlin L, et al. Short-segment percutaneous pedicle screw fixation with cement augmentation for tumor-induced spinal instability[J]. The Spine Journal, 2015, 15(7): 1609-1617.

	\bibitem{wilson1971glass}
	Wilson AD, Kent B. The glass-ionomer cement, a new translucent dental filling material[J]. Journal of Applied Chemistry and Biotechnology, 1971, 21(11): 313-313.

	\bibitem{nicholson1993study}
	Nicholson J, Hawkins S, Wasson E. A study of the structure of zinc polycarboxylate dental cements[J]. Journal of Materials Science: Materials in Medicine, 1993, 4: 32-35.

	\bibitem{sidhu2016review}
	Sidhu SK, Nicholson JW. A review of glass-ionomer cements for clinical dentistry[J]. Journal of functional biomaterials, 2016, 7(3): 16.

	\bibitem{ambard2006calcium}
	Ambard AJ, Mueninghoff L. Calcium phosphate cement: review of mechanical and biological properties[J]. Journal of Prosthodontics, 2006, 15(5): 321-328.

	\bibitem{newman2006survey}
	Newman TS, Yi H. A survey of the marching cubes algorithm[J]. Computers \& Graphics, 2006, 30(5): 854-879.

	\bibitem{no2014nanomaterials}
	No YJ, Roohani-Esfahani SI, Zreiqat H. Nanomaterials: the next step in injectable bone cements[J]. Nanomedicine, 2014, 9(11): 1745-1764.

	\bibitem{samad2011new}
	Samad HA, Jaafar M, Othman R, et al. New bioactive glass-ceramic: synthesis and application in PMMA bone cement composites[J]. Bio-medical materials and engineering, 2011, 21(4): 247-258.

	\bibitem{jeong2019bioactive}
	Jeong J, Kim JH, Shim JH, et al. Bioactive calcium phosphate materials and applications in bone regeneration[J]. Biomaterials research, 2019, 23(1): 4.

	\bibitem{tan2021biomaterial}
	Tan B, Tang Q, Zhong Y, et al. Biomaterial-based strategies for maxillofacial tumour therapy and bone defect regeneration[J]. International journal of oral science, 2021, 13(1): 9.

	\bibitem{li2024integrated}
	Li J, Yang Y, Sun Z, et al. Integrated evaluation of biomechanical and biological properties of the biomimetic structural bone scaffold: Biomechanics, simulation analysis, and osteogenesis[J]. Materials Today Bio, 2024, 24: 100934.

	\bibitem{shen2024visual}
	Shen L, Zhang Y, Wang X, et al. Visual simulation of bone cement blending and dynamic flow[C]//2024 IEEE International Conference on Bioinformatics and Biomedicine (BIBM): 2024: to appear.

	\bibitem{zhangBoneCementCMPB}
	Zhang Y, Shen L, Wang X, Frey S, Telea AC, Kosinka J. Bone Cement Flow Simulation: A Two-Phase Non-Newtonian Fluid Approach for Surgical Optimization[J]. Computer Methods and Programs in Biomedicine, under review.

